\input{../../../tools/stand-alone}
\Problem{Detector Dodging}

%% author:			Twan, Jasper
%% reviews:         -
%% text-completion:	80%
%% contest:			iwi2010
%% keywords:		geometry
%% difficulty:		2

\def\MineName{Monique}

{\StandaardZin}
As a result {\MineName} has vowed to dodge fares as often as she can.
However, in order for her not to be caught she does have to check in with her OV-chipcard whenever she takes the train.
The trick is to avoid checking out at the destination, checking out much closer to home instead.

To prevent suspicion {\MineName} always walks off the platform in a straight line.
However, this Saturday morning {\MineName} found herself on the train platform in Groningen, on her way to the IWI Programming Contest.
And unfortunately for her they had set up an enormous amount of more or less randomly positioned detectors.
She tried making a clean escape, but she could not avoid brushing against a detection rod.

The next time {\MineName} will be prepared!
Can you help her by finding the size (in degrees) of the largest arc over which there are no rods?

\Input
\begin{itemize}
 \item A line with a single positive integer $n < 10^6$, the number of detection rods.
 \item $n$ lines, each containing two integers, the $x$ and $y$ coordinates of each rod relative to {\MineName}'s current location. $|x|,|y|<10^6$.
\end{itemize}

\Output
\begin{itemize}
 \item One line containing the size of the largest arc (in degrees) over which there are no rods.
       The answer should be between $0$ and $360$, and have an error of at most $10^{-6}$ degrees.
\end{itemize}

\vfill % layout
\Example
