\input{../../../tools/stand-alone}
\Problem{Settle the Bill}

%% author:			Jasper
%% reviews:         -
%% text-completion:	0%
%% contest:			iwi2010
%% keywords:		example
%% difficulty:		1..5

\def\BillHero{Professor Bakker}

{\StandaardZin}
Unfortunately the new OV-chipcard does not allow for multiple people to travel on one card.
This is bad news for the Computer Science department as they frequently travel together, sharing the costs.
They have not settled the last few travel bills yet, expecting that in the long run everything would cancel out.
However, because of the economic crisis they agree to settle the bills now, once and for all.

%As they have not settled the last few travel bills yet (hoping that in the long run it would cancel out) they agree to settle them now, once and for all.

As a certain kind of laziness comes natural to every good computer scientist: they naturally want to minimize the number of transactions.
After a few all-nighters {\BillHero} has figured out that $n-1$ is an upper bound for the number of transactions needed to settle debts between $n$ persons.
His general theory of settlements is based on the assumption that the number of transactions over $x$ days is described by %$t(x) = \frac{x^{(n-1)}-1}{x-1}$.
$t(x) = \bigl(x^{(n-1)}-1\bigr)/\bigl(x-1\bigr)$.
In the optimal case where all transactions are settled in a single day this gives $\lim_{x\rightarrow 1}\bigl(x^{(n-1)}-1\bigr)/\bigl(x-1\bigr)=n-1$.

%\NOTTODO{More math mumbo-jumbo? E.g. $\lim_{x\rightarrow 1}\frac{x^{(n-1)}-1}{x-1}=n-1$.}
Some people think they can do better though.
Can they?

\Input
\begin{itemize}
 \item A line containing two positive integers $n < 20$ and $m < 400$, the number of people and the number of debts respectively.
 \item $m$ lines containing three integers $0 \leq f_i, t_i < n$ and $a_i < 10^7$, the zero-based index of the person who owes money, the zero-based index of the person to whom he owes money, and the amount of money owed in Euros.
\end{itemize}

\Output
\begin{itemize}
 \item One line containing \literaloutput{tight} if {\BillHero}'s bound is tight (exactly $n-1$ transactions are needed) in this case, or \literaloutput{loose} if the bound is not tight (in this case).
\end{itemize}

\Example
