\input{../../../tools/stand-alone}
\Problem{Downhill}

%% author:			Twan
%% reviews:         -
%% text-completion:	0%
%% contest:			iwi2010
%% keywords:		sort
%% difficulty:		3

\def\tspname{Paul}

{\StandaardZin}
Most commonly the OV-chipcard is used as a toy (4 years and older) or as a bookmark, in some cases it is even used to open locked doors.
This is why {\tspname}, a traveling salesman from New York, just knew that he had to get his hands on as many of these versatile tools as possible. % note: traveling is US, travelling is British
%Back home he visits a number of houses each day to sell his merchandise.

The streets in Manhattan, where {\tspname} works, form a regular grid on inclined plane.
There are numbered streets running east-west and numbered avenues running north-south.
% wiki:
% Often, the numbered streets run east-west and the numbered avenues north-south, following the style adopted
{\tspname} has taken great care to plan an efficient route through the city, visiting all the houses of potential clients.

This Monday morning disaster struck: his car broke down.
It still runs, but just barely.
He can go no faster than twenty miles per hour, and only downhill.

Fortunately, Manhattan was built on a hill and {\tspname} lives at the highest point,
at the intersection of 1st street and 1st avenue.
%The intersection of 1st avenue and 1st street is at the top of a hill.
%So he is still able to drive south to 2nd street, or east to 2nd avenue.
So he is still able to drive south to 2nd street, 3rd street, etc.; or east to 2nd avenue, 3rd avenue, etc..
His regular route is no longer an option, since then he would also have to drive uphill.
{\tspname} would still like to visit as many houses as possible, so he can earn enough money to fix his car.

\Input
\begin{itemize}
 \item A line with a single natural number \voor{licht}{$n<10^4$}{$n<10^6$}, the number potential clients {\tspname} wants to visit.
 \item $n$ lines, each containing two positive integers $s_i,a_i < 10^9$, the street and avenue number of the intersections where a house is located.
       All houses are located at different intersections.
       \NOTTODO{ is dat `different intersections' nodig? anders is het een naar randgeval }
\end{itemize}

\Output
\begin{itemize}
 \item One line containing a single integer, the maximal number of houses {\tspname} can visit.
\end{itemize}

\vfill % layout
\Example
